Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-01-30 paper/rebuttal/egrebuttal.tex

\paragraph{R2: Faster than State of the Art?}
%We report the average correction times for novice users in lines 756-765. Figure 7 (column 3) shows VI reduction after 30 minutes and the slopes in figure 6 also indicate better performance for GP. However, this presentation is not ideal and 
`Faster' here considers both how long each correction takes, and the likely VI reduction from that correction. Our approach has comparable correction time to the state-of-the-art Focused Proofreading appraoch, but a significantly greater VI reduction per correction (7.5$\times$). Our presentation of this discovery could have been improved. We will add Table~\ref{tab:correctiontimes} to make this clearer (previously reported in lines 756-765, slopes in Fig.~6, and column 3 in Fig.~7).

\begin{table}[h]
\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). For comparable correction time, our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
Approach & \makecell{Time Per Correction (s)} & \makecell{VI Reduction Per Minute} \\
\midrule
\emph{Dojo} & 30.5 & -0.002 \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 \\
\emph{GP} & 6.2 & 0.00173 \\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}

\paragraph{R2: Reproducibility}
R2 expresses concerns regarding reproducibility. As per line 847, we have promised to release all our code and data, and we disclose all parameters.

\paragraph{R2: How were Optimal Parameters chosen?}
The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating on previously-unseen test data (lines 585-586, supplemental Sec. 1.3). The \textbf{input border is dilated by 5 pixels} to consider slight edge ambiguities and to cover extra-cellular space between segments in high-resolution electron microscopy data (lines 308-310). During merge error detection, \textbf{labels are dilated by 20 pixels} prior to finding potential borders (line 323) with border-seeded watershed---this way the borders tend to attach to real membrane boundaries (lines 364-366). As we use a CNN, there are many additional parameters; we consider choosing these effectively to be an open problem, and for this we used learned experience and local brute-force searches.
%Here, we list all parameters and describe how their values are obtained. We will synchronize this information with the paper.
%We define several parameters in the paper. However, we agree with reviewer 2 that finding the optimal values requires better explanations and we will synchronize the following information with the paper.

@@

%\begin{table}[h]
%\caption{Parameters of GP, their values and how these values are obtained.}%While the training of our classifier is more expensive, testing accuracy is superior. }
%\resizebox{\linewidth}{!}{
%\begin{tabular}{l}
%\toprule
%Threshold $p_t=0.95$, Observed on previously unseed testing data (lines 585-586, supplemental Sec. 1.3) \\ 
%\bottomrule
%\end{tabular} 
%}
%\label{tab:parameters}
%\end{table}

\paragraph{R3: Training Datasets---U-net vs.~GP?}
R3 raises the question of whether our GP approach was trained on the same data as membrane detection (U-net). There was no overlap (Tab.~\ref{tab:trainingdata}).

\begin{table}[h]
\caption{Training data of membrane detection vs.~training data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
%Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
Dataset & \makecell{Training Set\\U-Net} & \makecell{Training Set\\GP} \\ 
\midrule
\makecell{\emph{L. Cylinder}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} \\ 
\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1000\times1000\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
\makecell{\emph{CREMI A/B/C}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} \\ 
\bottomrule
\end{tabular} 
}
\label{tab:trainingdata}
\end{table}

\paragraph{R3: Merge Error Detection}
R3 requests a better explanation of the merge error detection. We have updated Figure 4 in the main paper to include the watershed seeds (Fig. 1). We will also add a pseudo code version of the algorithm to the supplemental material to promote understanding (Alg. \ref{code:mergeerror}).

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v5.pdf}
\caption{Updated Figure 4 including the random watershed seeds (yellow).}
\label{fig:merge_error}
\end{figure}

\begin{algorithm}
\caption{Merge Error Detection for label \emph{l}}\label{code:mergeerror}
\begin{algorithmic}[1]
%\State{mergeErrors = []}
%\For{\emph{l} in $\forall$labels}
	\State{$l_d$ = dilate(\emph{l}, 20)}
	%\For{N iterations}
		%\State{$s_1$,$s_2$ = findRandomSeeds($l_d$)}
		\State{border = watershed($l_d$, $\text{seeds}_\text{random}$)}
		%\State{border = findBorder(ws)}
		\State{$p_\text{split}$ = rank(border)}
		\State{$p_\text{merge}$ = $1-p_\text{split}$}
		%\State{correct($\max p_\text{merge}$)}
	%\EndFor

\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Merge Error Detection for one label}\label{code:mergeerror2}
\begin{algorithmic}[1]
%\State{mergeErrors = []}
%\For{\emph{l} in $\forall$labels}
	\State{dilate label}
	\For{N iterations}
		\State{watershed (randomly seeded)}
		\State{$p$ = rank border using split error CNN}
		\State{$p_\text{merge}$ = $1-p$}	
	\EndFor
	\State{find max $p_\text{merge}$}

\end{algorithmic}
\end{algorithm}

### 2017-01-30 paper/rebuttal/egrebuttal.tex

%\begin{table}[h]
%\caption{Parameters of GP, their values and how these values are obtained.}%While the training of our classifier is more expensive, testing accuracy is superior. }
%\resizebox{\linewidth}{!}{
%\begin{tabular}{l}
%\toprule
%Threshold $p_t=0.95$, Observed on previously unseed testing data (lines 585-586, supplemental Sec. 1.3) \\ 
%\bottomrule
%\end{tabular} 
%}
%\label{tab:parameters}
%\end{table}

\paragraph{R3: Training Datasets---U-net vs.~GP?}
R3 raises the question of whether our GP approach was trained on the same data as membrane detection (U-net). There was no overlap (Tab.~\ref{tab:trainingdata}).

\begin{table}[h]
\caption{Training data of membrane detection vs.~training data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
%Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
Dataset & \makecell{Training Set\\U-Net} & \makecell{Training Set\\GP} \\ 
\midrule
\makecell{\emph{L. Cylinder}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} \\ 
\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1000\times1000\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
\makecell{\emph{CREMI A/B/C}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} \\ 
\bottomrule
\end{tabular} 
}
\label{tab:trainingdata}
\end{table}

\paragraph{R3: Merge Error Detection}
R3 requests a better explanation of the merge error detection (Sec. 3.2). We have updated Figure 4 in the main paper to be more descriptive (Fig. 1). We will also add pseudo code of the algorithm to the supplemental material to promote understanding (Alg. \ref{code:mergeerror}).

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
\caption{Merge errors are identified by generating randomly-seeded watershed borders within a dilated label segment. Then, each border is individually rated using the split error CNN by inverting the probability score.}
\label{fig:merge_error}
\end{figure}

%\begin{algorithm}
%\caption{Merge Error Detection for label \emph{l}}\label{code:mergeerror}
%\begin{algorithmic}[1]
%%\State{mergeErrors = []}
%%\For{\emph{l} in $\forall$labels}
%	\State{$l_d$ = dilate(\emph{l}, 20)}
%	%\For{N iterations}
%		%\State{$s_1$,$s_2$ = findRandomSeeds($l_d$)}
%		\State{border = watershed($l_d$, $\text{seeds}_\text{random}$)}
%		%\State{border = findBorder(ws)}
%		\State{$p_\text{split}$ = rank(border)}
%		\State{$p_\text{merge}$ = $1-p_\text{split}$}
%		%\State{correct($\max p_\text{merge}$)}
%	%\EndFor
%
%\end{algorithmic}
%\end{algorithm}

\begin{algorithm}
\caption{Merge Error Detection for a label \emph{l}}\label{code:mergeerror}
\begin{algorithmic}[1]
%\State{mergeErrors = []}
%\For{\emph{l} in $\forall$labels}
	\State{$l_d$ = \textbf{dilate}(\emph{l}, 20)}
	\State{invImage = \textbf{invert}(image)}
	\For{N iterations}
		\State{$s_1$,$s_2$ = \textbf{randomSeeds}($l_d$)}
		\State{wsImage = \textbf{watershed}(invImage, $l_d$,$s_1$,$s_2$)}
		\State{border = \textbf{border}(wsImage)}
		\State{$p$ = \textbf{rank}(border)}
		\State{$p_\text{merge}$ = $1-p$}	
	\EndFor
	\State{\textbf{find}(max $p_\text{merge})$}

### 2017-01-30 paper/rebuttal/egrebuttal.tex

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal for `Guided Proofreading of Automatic Segmentations for Connectomics'}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

Thank you for your time and constructive comments. We will fix all minor issues.

\vspace{-1mm}

\paragraph{R2: Quantitative Evaluation}
R2 requests an objective quantitative evaluation. Our `automatic' and `oracle' experiments are exactly this. We define such experiments in lines 573--590 and report the results in Fig.~6, Fig.~7, and lines 792--818 (also in supplemental Sec.~2 and 3). These evaluations use the quantitative VI metric against a ground truth segmentation, with no user in the loop.

\vspace{-1mm}

\paragraph{R2: Faster than State of the Art?}
%We report the average correction times for novice users in lines 756-765. Figure 7 (column 3) shows VI reduction after 30 minutes and the slopes in figure 6 also indicate better performance for GP. However, this presentation is not ideal and 
`Faster' here considers both how long each correction takes, and the likely VI reduction from that correction. Our approach has comparable correction time to the state-of-the-art Focused Proofreading approach, but a significantly greater VI reduction per correction (7.5$\times$). We agree that the presentation of this comparison was not ideal. We will add Table~\ref{tab:correctiontimes} to make this clearer (previously reported in lines 756-765, slopes in Fig.~6, and column 3 in Fig.~7).

@@

\begin{table}[h]
\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). For comparable correction time, our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
Approach & \makecell{Time Per Correction (s)} & \makecell{VI Reduction Per Minute} \\
\midrule
\emph{Dojo} & 30.5 & -0.002 \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 \\
\emph{GP} & 6.2 & 0.00173 \\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}

\vspace{-5mm}

\paragraph{R2: Reproducibility}
R2 expresses concerns regarding reproducibility. As per line 847, we have promised to release all our code including trained models and data, and we disclose all parameters.

\vspace{-1mm}

\paragraph{R2: How were Optimal Parameters chosen?}
The \textbf{threshold $p_t=0.95$} was observed to be stable when evaluating VI reduction on previously-unseen test data (lines 585-586, supplemental Sec. 1.3). The \textbf{input border is dilated by 5 pixels} to consider slight edge ambiguities and extra-cellular space in high-resolution electron microscopy data (lines 308-310). During merge error detection, \textbf{labels are dilated by 20 pixels} prior to finding potential borders (line 323) with border-seeded watershed---this way the borders tend to attach to real membrane boundaries (lines 364-366). As we use a CNN, there are many additional parameters; we consider choosing these effectively to be an open problem, and for this we used learned experience and local brute-force searches on separate training data.
%Here, we list all parameters and describe how their values are obtained. We will synchronize this information with the paper.
%We define several parameters in the paper. However, we agree with reviewer 2 that finding the optimal values requires better explanations and we will synchronize the following information with the paper.

@@

%
%\begin{itemize}
%\item \textbf{Threshold $p_t$.} The threshold $p_t=0.95$ was observed to be stable when evaluating on previously unseen testing data (lines 585-586, supplemental Sec. 1.3).
%\item \textbf{Dilated Boundary Input.} We dilate the border between segments by 5 pixels to consider slight edge ambiguities and to cover extra-cellular space between segments in high-resolution electron microscopy data (lines 308-310).
%\item \textbf{Dilated Label.} During merge error detection, labels are dilated by 20 pixels prior to finding potential borders (line 323) with border-seeded watershed. By doing so, the borders tend to attach to real membrane boundaries (lines 364-366).
%\end{itemize}

%\begin{table}[h]
%\caption{Parameters of GP, their values and how these values are obtained.}%While the training of our classifier is more expensive, testing accuracy is superior. }
%\resizebox{\linewidth}{!}{
%\begin{tabular}{l}
%\toprule
%Threshold $p_t=0.95$, Observed on previously unseed testing data (lines 585-586, supplemental Sec. 1.3) \\ 
%\bottomrule
%\end{tabular} 
%}
%\label{tab:parameters}
%\end{table}

\paragraph{R3: Training Datasets---U-net vs.~GP?}
R3 raises the question of whether our GP approach was trained on the same data as membrane detection (U-net). There was no overlap (Tab.~\ref{tab:trainingdata}).

\vspace{-1mm}

\begin{table}[h]
\caption{Training data of membrane detection vs.~training data of GP vs.~test data (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
\vspace{-1mm}
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
%Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
\makecell{Training Set\\U-Net / GALA} & \makecell{Training Set\\GP} & \makecell{Test Set\\GP}\\ 
\midrule
\makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} &
\makecell{$\text{L. Cylinder}_\text{test}$\\($2048\times2048\times50$vx)}
\\ 
\makecell{AC4 excl. test\\ ($1024\times1024\times90$vx)} &  \makecell{L. Cylinder\\($2048\times2048\times250$vx)} &
\makecell{$\text{AC4}_\text{test}$ subvolume\\($400\times400\times10$vx)} \\ 
\makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} &
\makecell{$\text{CREMI A/B/C}_\text{test}$\\($1250\times1250\times15$vx)} \\ 
\bottomrule
\end{tabular} 
}
\label{tab:trainingdata}
\end{table}

%\begin{table}[h]
%\caption{Training data of membrane detection vs.~training data of GP (for supplemental material).}%While the training of our classifier is more expensive, testing accuracy is superior. }
%\vspace{-1mm}
%\resizebox{\linewidth}{!}{
%\begin{tabular}{lrrrr}
%\toprule
%%Dataset & \makecell{Training Set\\Membrane Detection (U-Net)} & \makecell{Training Set\\Guided Proofreading} \\ 
%Dataset & \makecell{Training Set\\U-Net} & \makecell{Training Set\\GP} \\ 
%\midrule
%\makecell{\emph{$\text{L. Cylinder}_\text{test}$}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{L. Cylinder\\($2048\times2048\times250$vx)} \\ 
%\makecell{\emph{AC4 subvolume}\\~} & \makecell{AC4 excl. test\\ ($1000\times1000\times90$vx)} &  \makecell{L. Cylinder\\ ($2048\times2048\times250$vx)} \\ 
%\makecell{\emph{CREMI A/B/C}\\~} & \makecell{AC3+AC4\\($1024\times1024\times175$vx)} & \makecell{CREMI A/B/C\\($1250\times1250\times300$vx)} \\ 
%\bottomrule
%\end{tabular} 
%}
%\label{tab:trainingdata}
%\end{table}

\vspace{-5mm}

\paragraph{R3: Merge Error Detection}
R3 requests a better explanation of the merge error detection (Sec. 3.2). We have updated Fig. 4 in the main paper to be more clear (Fig. 1). We will also add pseudo code of the algorithm to the supplemental material to promote understanding (Alg. \ref{code:mergeerror}).

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{gfx/merge_error_v6.pdf}
\vspace{-6mm}
\caption{Potential borders are generated on inverted images by randomly placing watershed seeds (green) on the boundary of a dilated segment. The best ranked seeds and border (both in red) result in the shown error correction.}
\label{fig:merge_error}
\end{figure}

\vspace{-5mm}

@@

%\begin{algorithm}
%\caption{Merge Error Detection for label \emph{l}}\label{code:mergeerror}
%\begin{algorithmic}[1]
%%\State{mergeErrors = []}
%%\For{\emph{l} in $\forall$labels}
%	\State{$l_d$ = dilate(\emph{l}, 20)}
%	%\For{N iterations}
%		%\State{$s_1$,$s_2$ = findRandomSeeds($l_d$)}
%		\State{border = watershed($l_d$, $\text{seeds}_\text{random}$)}
%		%\State{border = findBorder(ws)}
%		\State{$p_\text{split}$ = rank(border)}
%		\State{$p_\text{merge}$ = $1-p_\text{split}$}
%		%\State{correct($\max p_\text{merge}$)}
%	%\EndFor
%
%\end{algorithmic}
%\end{algorithm}

\begin{algorithm}
\caption{Merge Error Detection for a label \emph{l}}\label{code:mergeerror}
\begin{algorithmic}[1]
%\State{mergeErrors = []}
%\For{\emph{l} in $\forall$labels}
	\State{$l_d$ = \textbf{dilate}(\emph{l}, 20)}
	\State{invImage = \textbf{invert}(image)}
	\For{N iterations}
		\State{$s_1$, $s_2$ = \textbf{randomSeedsOnBoundary}($l_d$)}
		\State{wsImage = \textbf{watershed}(invImage, $l_d$, $s_1$, $s_2$)}
		\State{border = \textbf{border}(wsImage)}
		\State{$p$ = \textbf{rank}(border)}
		\State{$p_\text{merge}$ = $1-p$}	
	\EndFor
	\State{\textbf{find}(max $p_\text{merge})$}
